Using the UK Biobank as a global reference: application to measuring ancestry diversity from GWAS summary statistics

### 2021-10-24 paper-ancestry-prop.tex
save

[TODO]

@@

%\clearpage

@@

\clearpage
%\section*{Supplementary Materials}
%
%\renewcommand{\thefigure}{S\arabic{figure}}
%\setcounter{figure}{0}
%\renewcommand{\thetable}{S\arabic{table}}
%\setcounter{table}{0}

>>>>

The newest version of R package bigsnpr can be installed from GitHub (see \url{https://github.com/privefl/bigsnpr}).
The set of reference allele frequencies for 5,816,590 genetic variants across 20 diverse ancestry groups we create here can be downloaded from \url{https://figshare.com/ndownloader/files/31163785}.
All code used for this paper is available at \url{https://github.com/privefl/freq-ancestry/tree/main/code}. 
We have extensively used R packages bigstatsr and bigsnpr \cite[]{prive2017efficient} for analyzing large genetic data, packages from the future framework \cite[]{bengtsson2020unifying} for easy scheduling and parallelization of analyses on the HPC cluster, and packages from the tidyverse suite \cite[]{wickham2019welcome} for shaping and visualizing results.

@@

@@
